Four reasons your build is slow

### 2019-01-17 paper.tex
Change subtitle.
spelling

If you develop software, or even if you compile it, you probably run
into software that's slow to build. This problem is such a cliche that
it appears in comics, but it's also such a problem that companies
routinely outfit developers with the beefiest machines possible---all
to compile software projects faster. Fortunately, for most systems and
languages, compiling software is a classic example of embarassing
parallelism. As a result, developers who spend much of their time
compiling large software projects use highly parallel systems to do so
\cite{regehr-tweet}.

@@

\section{Analysis tool}
\label{sec:analysis}
In this section we describe the tools we use to analyse make builds, diagnose problems related
to parallelism, and identify places for improvement. In section \ref{sec:makeanalysis} we
discuss the modified version of GNU Make \cite{gnumakemanual} we use to record enough information about a
project's build to reconstruct the build graph during a post-mortem analysis.
In section \ref{sec:straceinstr} we discuss how we use a slightly modified version of strace to
record all of the system calls made during the project's build and then use the system calls
to determine the real dependencies of the build. In section \ref{sec:revisegraphs} we discuss
how to combine the information from these two tools to transform a build graph into
a new graph with potentially more parallelism.

@@

\subsection{Expensive command}
\label{sec:expensive}

@@

Facebook's zstd project \cite{zstd1.3.7} has a build that exhibits this property.  When we used our tool to analyse
the span of zstd's build we saw that it is dominated by a single call to cc; see fig. \ref{code:cc1}.

@@

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  cc \$(FLAGS) common/debug.c \textrm{\emph{29 more .c files}}
    -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for aproximately 100\% of zstd's span when the command in fig. \ref{code:cc1} is removed.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}
If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

Some projects may exhibit ample potential parallelism but not achieve
that potential parallelism in practice.  LLVM~\citep{LLVM:CGO04} is
the largest project we analysed, with a calculated work of
approximately 12584 seconds, or 3.5 hours, and a predicted span of 305
seconds, or 5 minutes (\verb|strace| instrumentation was disabled for
this measurement). With a work of 3.5 hours and a span of 5 minutes,
LLVM has a parallelism of about 41.

@@

This demonstrates that our automatic prediction is accurate out to a
large number of parallel jobs, but also that the LLVM build fails to
achieve as much parallel scaling as we would hope. This suggests that
although the build system is able to provide adequate parallelism, the
underlying Linux OS and \verb|make| job scheduling fail to take
advantage. To enable better scaling, potential sources of contention
such as the filesystem must be examined.

>>>>

If you develop software, or even if you compile it, you probably run
into software that's slow to build. This problem is such a cliche that
it appears in comics, but it's also such a problem that companies
routinely outfit developers with the beefiest machines possible---all
to compile software projects faster. Fortunately, for most systems and
languages, compiling software is a classic example of embarrassing
parallelism. As a result, developers who spend much of their time
compiling large software projects use highly parallel systems to do so
\cite{regehr-tweet}.

@@

\section{Analysis tool}
\label{sec:analysis}
In this section we describe the tools we use to analyze make builds, diagnose problems related
to parallelism, and identify places for improvement. In section \ref{sec:makeanalysis} we
discuss the modified version of GNU Make \cite{gnumakemanual} we use to record enough information about a
project's build to reconstruct the build graph during a post-mortem analysis.
In section \ref{sec:straceinstr} we discuss how we use a slightly modified version of strace to
record all of the system calls made during the project's build and then use the system calls
to determine the real dependencies of the build. In section \ref{sec:revisegraphs} we discuss
how to combine the information from these two tools to transform a build graph into
a new graph with potentially more parallelism.

@@

\subsection{Too large command}
\label{sec:expensive}

@@

Facebook's zstd project \cite{zstd1.3.7} has a build that exhibits this property.  When we used our tool to analyze
the span of zstd's build we saw that it is dominated by a single call to cc; see fig. \ref{code:cc1}.

@@

If this call is no longer part of the span, the new span is similarly dominated by another single call to cc;
see fig. \ref{code:cc2}.
\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  cc \$(FLAGS) common/debug.c \textrm{\emph{29 more .c files}}
    -o libzstd.so.1.3.7
\end{Verbatim}
\caption{A long running cc command which was responsible for approximately 100\% of zstd's span when the command in fig. \ref{code:cc1} is removed.
This command compiled and linked 30 files.}
\label{code:cc2}
\end{figure}
If neither of these calls are members of the build's span, then our tool predicts the span would be
approximately 7.2 seconds rather than 39 seconds, as with the original span, or 37 seconds, as with the second span.
This is about an 80\% reduction in the build's span, and the parallelism improves from 2.98 to 16.

@@

Some projects may exhibit ample potential parallelism but not achieve
that potential parallelism in practice.  LLVM~\citep{LLVM:CGO04} is
the largest project we analyzed, with a calculated work of
approximately 12584 seconds, or 3.5 hours, and a predicted span of 305
seconds, or 5 minutes (\verb|strace| instrumentation was disabled for
this measurement). With a work of 3.5 hours and a span of 5 minutes,
LLVM has a parallelism of about 41.

@@

This demonstrates that our automatic prediction is accurate out to a
large number of parallel jobs, but also that the LLVM build fails to
achieve as much parallel scaling as we would hope. This suggests that
although the build system is able to provide adequate parallelism, the
underlying Linux OS and \verb|make| job scheduling fail to take
advantage. To enable better scaling, potential sources of contention
such as the file system must be examined.
